\documentclass[12pt, titlepage]{article}
\usepackage[shortlabels]{enumitem}
\usepackage{comment}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{hyperref}
\usepackage{float}
\usepackage{soul}
\usepackage{changepage}
\usepackage{graphicx}
\hypersetup{
    colorlinks,
    citecolor=blue,
    filecolor=black,
    linkcolor=red,
    urlcolor=blue
}
\usepackage[round]{natbib}

\input{../Comments}
\input{../Common}

\begin{document}

\title{Project Title: System Verification and Validation Plan for \progname{}} 
\author{\authname}
\date{\today}
	
\maketitle

\pagenumbering{roman}

\section{Revision History}

\begin{tabularx}{\textwidth}{p{3cm}p{2cm}X}
\toprule {\bf Date} & {\bf Version} & {\bf Developer - Notes}\\
\midrule
Oct 31 & 1.0 & Edwin Do - Added section 4 for V\&V Plan\\
Date 2 & 1.1 & Notes\\
\bottomrule
\end{tabularx}

\newpage

\tableofcontents

\listoftables
\wss{Remove this section if it isn't needed}

\listoffigures
\wss{Remove this section if it isn't needed}

\newpage

\section{Symbols, Abbreviations and Acronyms}

\renewcommand{\arraystretch}{1.2}
\begin{tabular}{l l} 
  \toprule		
  \textbf{symbol} & \textbf{description}\\
  \midrule 
  T & Test\\
  SRS & Software Requirements Specifications \\
  VS & Visual Studio\\
  UWP & Universal Windows Platform\\
  \bottomrule
\end{tabular}\\

\wss{symbols, abbreviations or acronyms -- you can simply reference the SRS
  \citep{SRS} tables, if appropriate}

\newpage

\pagenumbering{arabic}

This document ... \wss{provide an introductory blurb and roadmap of the
  Verification and Validation plan}

\section{General Information}

\subsection{Summary}

\wss{Say what software is being tested.  Give its name and a brief overview of
  its general functions.}

\subsection{Objectives}

\wss{State what is intended to be accomplished.  The objective will be around
  the qualities that are most important for your project.  You might have
  something like: ``build confidence in the software correctness,''
  ``demonstrate adequate usability.'' etc.  You won't list all of the qualities,
  just those that are most important.}

\subsection{Relevant Documentation}

\wss{Reference relevant documentation.  This will definitely include your SRS
  and your other project documents (MG, MIS, etc).  You can include these even
  before they are written, since by the time the project is done, they will be
  written.}

\citet{SRS}

\section{Plan}
% RUBRIC
% 'Team member's roles for testing are clear;  
% This may involve switching roles between verification tasks 
% (say between SRS verification, hardware verification, and code verification).  
% Clear, specific and feasible plan for SRS verification; 
% Clear specific and feasible plan for Design verification; 
% Clear specific and feasible plan for implementation verification.  
% Automated testing and verification tools are specific.  
% Software validation plan is clear, specific and feasible.

% \wss{Introduce this section.   You can provide a roadmap of the sections to
%   come.}

  In this section of planning, it will outline our approaches to cover the requirements 
  outlined in various areas such as the SRS document, Hazard analysis document, our implementation and design. 
  Tools that will be used for automated unit testing and linting will also be introduced.\\

  The following topics will be covered:

  \begin{itemize}
    \item The verification and validation team along with their respective responsibilities
    \item Our approach towards the SRS Verification plan
    \item Our approach towards the Design Verification plan
    \item Implementation verification plan
    \item Any testing and verification tools we plan to use
  \end{itemize}


\subsection{Verification and Validation Team}

% \wss{You, your classmates and the course instructor.  Maybe your supervisor.
%   You shoud do more than list names.  You should say what each person's role is
%   for the project.  A table is a good way to summarize this information.}

  Below is a table outlining the members of the Verification and Validation team along with their respective responsibilities.
  Note that the listed responsibilities are only used as a guideline, responsibilities can shift between team members on a as-per-needed basis.

  \begin{table}[H]
    \centering
    \caption{Team and Responsibilities}
    \label{my-label}
    \begin{tabular}{|c|c|c|}
      \hline
      \textbf{Team Member} & \textbf{Role Name} & \textbf{Responsibilities}   \\ \hline
      Edwin Do & 
      \begin{tabular}{@{}c@{}}Software and SRS Tester\end{tabular} & 
      \begin{tabular}{@{}c@{}}Ensures that all requirements are valid \\ 
        and verified under the scope of software \\
        capabilities in this project and the SRS\end{tabular} \\ \hline
      
      Timothy Chen & 
      \begin{tabular}{@{}c@{}}Software Tester\end{tabular} & 
      \begin{tabular}{@{}c@{}}Ensures that all requirements are met \\ 
        and verified under the scope of software \\
        capabilities in this project\end{tabular} \\ \hline
      
      Tyler Magarelli & 
      \begin{tabular}{@{}c@{}}Software Tester\end{tabular} & 
      \begin{tabular}{@{}c@{}}Ensures that all requirements are met\\ 
        and verified under the scope of software \\
        capabilities in this project\end{tabular} \\ \hline
      
      Joseph Braun & 
      \begin{tabular}{@{}c@{}}Hardware Tester\end{tabular} & 
      \begin{tabular}{@{}c@{}}Ensures that all requirements are met \\ 
        and verified under the scope of hardware \\
        capabilities in this project\end{tabular} \\ \hline
      
      Abdul Nour Seddiki & 
      \begin{tabular}{@{}c@{}}Hardware Tester\end{tabular} & 
      \begin{tabular}{@{}c@{}}Ensures that all requirements are met \\ 
        and verified under the scope of hardware \\
        capabilities in this project\end{tabular} \\ \hline

      Dr. Hatem Zurob & 
      \begin{tabular}{@{}c@{}}Supervisor\end{tabular} & 
      \begin{tabular}{@{}c@{}}Ensures that all requirements are valid \\ 
        and meets the expected result\end{tabular} \\ \hline
    \end{tabular}
  \end{table}

\subsection{SRS Verification Plan}

% \wss{List any approaches you intend to use for SRS verification.  This may just
%   be ad hoc feedback from reviewers, like your classmates, or you may have
%   something more rigorous/systematic in mind..}

% \wss{Remember you have an SRS checklist}

\noindent To verify our SRS, our team intends on revisiting the SRS document on a bi-weekly basis to verify that 
the requirements are up to date and in sync with the project goal. This will also allow us to cover any
newly discover risks or hazards which will also be reflected in the Hazard Analysis document. Any new changes
within the two week window will be noted and discussed at the end to see if additional changes to the SRS document 
would be necessary. At each bi-weekly review, the team also plans on using the SRS checklist as a guideline throughout
the meeting.\\

\noindent  In addition, the team will use ad hoc feedback from reviewers such as classmates from our 4GA6 Capstone class as well
as instructor, supervisor and teaching assistants. This will act as a supplementary addition if any element of the SRS 
is out of date or missing.

\subsection{Design Verification Plan}

Our plans to verify our design document includes using the MIS checklist and reviews from our classmates. 
The MIS checklist will help our team ensure that the design logic helps us meet the requirements specified in 
the SRS document and cover any hazards or risks outlined in the Hazard analysis. The team will conduct an internal 
design review, by going over all the outlined requirements, risks and hazards and verifiying that the design does not
contain any logical flaws to the best of our abilities. \\

\noindent  In addition, the team will use the feedback from reviewers such as classmates from our 4GA6 Capstone class as well
as instructor, supervisor and teaching assistants. This will help further assist our team to ensure that the design is free from 
any logical flaws and is able to help meet the outlined requirements. 

% \wss{Plans for design verification}

% \wss{The review will include reviews by your classmates}

% \wss{Remember you have MG and MIS checklists}

\subsection{Implementation Verification Plan}

% [Point to other tests and unit testing plan]

Throughout the development phase of this project, the team will use GitHub Issues and pull requests to implement
various features. Each pull request will require at least two other team members to inspect and review the code 
ensuring that it meets the requirement and design discussed. 

% \wss{You should at least point to the tests listed in this document and the unit
%   testing plan.}

% \wss{In this section you would also give any details of any plans for static verification of
%   the implementation.  Potential techniques include code walkthroughs, code
%   inspection, static analyzers, etc.}

\subsection{Automated Testing and Verification Tools}

The final product will be an Universal Windows Platform (UWP) application built using Microsoft Visual Studio (VS) in C\# and XAML. \\

\noindent Majority of the project's testing will be conducted within VS. 
For unit testing, the team will use the built-in features of Unit Test Applications in VS to create unit tests projects and units tests.\\

\noindent Code coverage tests is also covered within the suite of tools available within VS. The team will be able to create testing suites and 
unit tests for the VS project. The team also plans on using the results of the code coverage
tests to identify which portion of the project's code not covered by our tests. Uncovered blocks of code can be colour-coded to signify to 
the developer that no current test covers that block of code. Other metrics such as number of lines covered, \% of a block covered will be 
summarized per code coverage project to help indicate where more testing efforts are needed. \\

\noindent Using Visual Studio's IDE extensions, the team plans on using SonarLint and CSharpier as its linter and formatting tool for C\# respectively. 

% \wss{What tools are you using for automated testing.  Likely a unit testing
%   framework and maybe a profiling tool, like ValGrind.  Other possible tools
%   include a static analyzer, make, continuous integration tools, test coverage
%   tools, etc.  Explain your plans for summarizing code coverage metrics.
%   Linters are another important class of tools.  For the programming language
%   you select, you should look at the available linters.  There may also be tools
%   that verify that coding standards have been respected, like flake9 for
%   Python.}

% \wss{The details of this section will likely evolve as you get closer to the
%   implementation.}

\subsection{Software Validation Plan}

% Use sample data provided by Dr.Zurob to ensure accuracy of data 

% \wss{If there is any external data that can be used for validation, you should
%   point to it here.  If there are no plans for validation, you should state that
%   here.}

\section{System Test Description}
	
\subsection{Tests for Functional Requirements}

\wss{Subsets of the tests may be in related, so this section is divided into
  different areas.  If there are no identifiable subsets for the tests, this
  level of document structure can be removed.}

\wss{Include a blurb here to explain why the subsections below
  cover the requirements.  References to the SRS would be good.}

\subsubsection{Area of Testing1}

\wss{It would be nice to have a blurb here to explain why the subsections below
  cover the requirements.  References to the SRS would be good.  If a section
  covers tests for input constraints, you should reference the data constraints
  table in the SRS.}
		
\paragraph{Title for Test}

\begin{enumerate}

\item{test-id1\\}

Control: Manual versus Automatic
					
Initial State: 
					
Input: 
					
Output: \wss{The expected result for the given inputs}

Test Case Derivation: \wss{Justify the expected value given in the Output field}
					
How test will be performed: 
					
\item{test-id2\\}

Control: Manual versus Automatic
					
Initial State: 
					
Input: 
					
Output: \wss{The expected result for the given inputs}

Test Case Derivation: \wss{Justify the expected value given in the Output field}

How test will be performed: 

\end{enumerate}

\subsubsection{Area of Testing2}

...

\subsection{Tests for Nonfunctional Requirements}

\wss{The nonfunctional requirements for accuracy will likely just reference the
  appropriate functional tests from above.  The test cases should mention
  reporting the relative error for these tests.}

\wss{Tests related to usability could include conducting a usability test and
  survey.}

\subsubsection{Area of Testing1}
		
\paragraph{Title for Test}

\begin{enumerate}

\item{test-id1\\}

Type: 
					
Initial State: 
					
Input/Condition: 
					
Output/Result: 
					
How test will be performed: 
					
\item{test-id2\\}

Type: Functional, Dynamic, Manual, Static etc.
					
Initial State: 
					
Input: 
					
Output: 
					
How test will be performed: 

\end{enumerate}

\subsubsection{Area of Testing2}

...

\subsection{Traceability Between Test Cases and Requirements}

\wss{Provide a table that shows which test cases are supporting which
  requirements.}

\section{Unit Test Description}

\wss{Reference your MIS and explain your overall philosophy for test case
  selection.}  
\wss{This section should not be filled in until after the MIS has
  been completed.}

\subsection{Unit Testing Scope}

\wss{What modules are outside of the scope.  If there are modules that are
  developed by someone else, then you would say here if you aren't planning on
  verifying them.  There may also be modules that are part of your software, but
  have a lower priority for verification than others.  If this is the case,
  explain your rationale for the ranking of module importance.}

\subsection{Tests for Functional Requirements}

\wss{Most of the verification will be through automated unit testing.  If
  appropriate specific modules can be verified by a non-testing based
  technique.  That can also be documented in this section.}

\subsubsection{Module 1}

\wss{Include a blurb here to explain why the subsections below cover the module.
  References to the MIS would be good.  You will want tests from a black box
  perspective and from a white box perspective.  Explain to the reader how the
  tests were selected.}

\begin{enumerate}

\item{test-id1\\}

Type: \wss{Functional, Dynamic, Manual, Automatic, Static etc. Most will
  be automatic}
					
Initial State: 
					
Input: 
					
Output: \wss{The expected result for the given inputs}

Test Case Derivation: \wss{Justify the expected value given in the Output field}

How test will be performed: 
					
\item{test-id2\\}

Type: \wss{Functional, Dynamic, Manual, Automatic, Static etc. Most will
  be automatic}
					
Initial State: 
					
Input: 
					
Output: \wss{The expected result for the given inputs}

Test Case Derivation: \wss{Justify the expected value given in the Output field}

How test will be performed: 

\item{...\\}
    
\end{enumerate}

\subsubsection{Module 2}

...

\subsection{Tests for Nonfunctional Requirements}

\wss{If there is a module that needs to be independently assessed for
  performance, those test cases can go here.  In some projects, planning for
  nonfunctional tests of units will not be that relevant.}

\wss{These tests may involve collecting performance data from previously
  mentioned functional tests.}

\subsubsection{Module ?}
		
\begin{enumerate}

\item{test-id1\\}

Type: \wss{Functional, Dynamic, Manual, Automatic, Static etc. Most will
  be automatic}
					
Initial State: 
					
Input/Condition: 
					
Output/Result: 
					
How test will be performed: 
					
\item{test-id2\\}

Type: Functional, Dynamic, Manual, Static etc.
					
Initial State: 
					
Input: 
					
Output: 
					
How test will be performed: 

\end{enumerate}

\subsubsection{Module ?}

...

\subsection{Traceability Between Test Cases and Modules}

\wss{Provide evidence that all of the modules have been considered.}
				
\bibliographystyle{plainnat}

\bibliography{../../refs/References}

\newpage

\section{Appendix}

This is where you can place additional information.

\subsection{Symbolic Parameters}

The definition of the test cases will call for SYMBOLIC\_CONSTANTS.
Their values are defined in this section for easy maintenance.

\subsection{Usability Survey Questions?}

\wss{This is a section that would be appropriate for some projects.}

\newpage{}
\section*{Appendix --- Reflection}

The information in this section will be used to evaluate the team members on the
graduate attribute of Lifelong Learning.  Please answer the following questions:

\begin{enumerate}
  \item 
  \item 
\end{enumerate}

\end{document}